Deriving Multi-Headed Projective Dependency Parses \\ from Link Grammar Parses

### 2014-05-27 doc/LinksToDAG.tex
list gomez-rodriguez & nivre properties (need to check against their paper)

\documentclass[11pt]{article}
\usepackage{acl2014}
\usepackage{times}
\usepackage{url}
\usepackage{latexsym}
\usepackage{amsmath}

@@

@@

\section{Introduction}
\todo{Intro}
Projective dependency parsing is the task of mapping a sentence to a directed acyclic graph.  
Link parsing in contrast produces a multiheaded planar graph with undirected edges, where every edge has a label describing the relationship between two constituents in a parse. In this paper we explore whether these relationships include dependencies, and whether the multiheadedness of the link grammar offers additional dependency relationships not found in other corpora.

>>>>

\documentclass[11pt]{article}
\usepackage{acl2014}
\usepackage{times}
\usepackage{url}
\usepackage{latexsym}
\usepackage{amsmath}
\usepackage{xspace}

@@

% \newcommand{\root}{\texttt{\$}}

@@

\section{Introduction}
\todo{Intro}

Dependency parsing maps a sentence to a directed graph whose vertices are the words $1, 2, \ldots, n$ of the sentence along with a distinguished ``root'' vertex 0.  A labeled directed edge $u \stackrel{L}{\rightarrow} v$ or $v \stackrel{L}{\leftarrow} u$ indicates that the ``child'' $v$ is some kind of argument or modifier of its ``parent'' $u$.  The edge label $L$ indicates the specific syntactic or semantic relationship between the two words.  In the special case $u=0$, the edge designates $v$ as playing some special top-level role in the sentence, e.g., as the main verb.  The case $v=0$ is not allowed.

As recently discussed by \newcite{gomez-rodriguez_divisible_2013}, one might place several optional requirements on the graph:
\begin{itemize}
\item acyclic (there are no directed cycles)
\item connected (for every pair of words $u,v$, there is an undirected path between them)
\item accessible (for every word $v\neq 0$, there is a directed path from 0 to $v$)
\item planar (no ``crossing edges'': if there is an edge between $u$ and $v$, then there is no edge between $i$ and $j$ where $u < i < v$ and not $u \leq j \leq v$)
\item single-headed (each $v\neq 0$ has at most one parent)
\end{itemize}
It is common to impose all of these requirements at once, leading to a {\em projective dependency parser} that produces projective, rooted trees.  However, parsing algorithms can be devised that relax any or all of the requirements \cite{gomez-rodriguez_divisible_2013}.

In this paper, we are interested in relaxing the requirement of single-headedness.
\NoteJE{discuss why.  Later, explain why our task isn't trivial.  We could just orient all edges from left to right, but we want to be consistent.}

Link parsing in contrast produces a multiheaded planar graph with undirected edges, where every edge has a label describing the relationship between two constituents in a parse. In this paper we explore whether these relationships include dependencies, and whether the multiheadedness of the link grammar offers additional dependency relationships not found in other corpora.
